% LaTeX resume using res.cls
\documentclass[margin]{res}
\setlength{\textwidth}{5.1in}
\usepackage{hyperref}

\begin{document}

\newcommand\quelle[1]{{%
      \unskip\nobreak\hfil\penalty50
      \hskip2em\hbox{}\nobreak\hfil#1%
      \parfillskip=0pt \finalhyphendemerits=0 \par}}

 \moveleft.5\hoffset\centerline{\large\bf Ernest John Kirstein IV}
 \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
 \moveleft.5\hoffset\centerline{glank314@gmail.com $\bullet$ (919)760-5193 $\bullet$ https://github.com/glank}
 \moveleft.5\hoffset\centerline{Apt. 1 210 Hudson Street $\bullet$ Hoboken, NJ 07030}

\begin{resume}

\section{EDUCATION}
	{\sl M.S.  Software Engineering}\\
	Monmouth University Graduate School\\
	May 2015 \vspace{5px}\\
	{\sl B.S.  Software Engineering} and {\sl B.S. Mathematics}\\
	Monmouth University Honors School, {\sl Cum Laude}\\
	January 2014
	
\section{HONORS AND \\ AWARDS}
	Member of Phi Eta Sigma Honors Society\\
	Member of Mensa\\
	Software Engineering Department Academic Excellence Award (Undergraduate), Monmouth University 2013
	
\section{SKILLS AND\\EXPERTISE}
	{\sl Languages:}  Python (2 years), Java (5+ years), C/C++, PHP, JavaScript\\
	{\sl IDEs:}  Vim, Eclipse, Visual Studio\\
	{\sl Operating Systems:}  Windows XP, Vista, and 7; Ubuntu and CentOS Linux

\section{EXPERIENCE} 
	{\sl Software Engineer} \hfill April 2015 - Now \\
	Google \hfill Ashesh Bakshi\\
	\quelle{asheshb@google.com}
	\begin{itemize}  \itemsep -2pt
		\item Improving data review process.
	\end{itemize}

	{\sl Math and Computer Science Tutor} \hfill October 2014 - April 2015\\
	Monmouth PAC \hfill Buryl Fortney\\
	{\sl pro bono} \hfill s0786435@monmouth.edu
	\begin{itemize}  \itemsep -2pt
		\item Tutoring high school students in math and programming.
		\item Planning and teaching the advance CS class.
	\end{itemize}

	{\sl Volunteer} \hfill October 2014 - April 2015\\
	Animal Rescue Force \hfill Susan\\
	{\sl pro bono} \hfill (732) 257-7559
	\begin{itemize}  \itemsep -2pt
		\item Walking and cleaning up after pets.
		\item Collecting donations.
	\end{itemize}

	{\sl Software Engineer} \hfill June 2014 - February 2015\\
	Discovery Data \hfill Claudio Diaz\\
	Salary: \$50k \hfill
	\begin{itemize}  \itemsep -2pt
		\item Requirements gathering in iterative development.
		\item Using and debugging data hygiene systems.
		\item Process improvement and automation.
	\end{itemize}
	
	{\sl Jr. Software Engineer} \hfill June 2013 - June 2014 \\
	Discovery Data \hfill Claudio Diaz\\
	Pay Rate: \$15/hr \hfill
	\begin{itemize}  \itemsep -2pt
		\item Maintaining and developing full-stack systems.
		\item Writing web scrapers in Python.
	\end{itemize}
	
	{\sl Software Developer} \hfill Sept 2011 - August 2013 \\
	Monmouth University \hfill Cui Yu\\
	Pay Rate: Approx. \$10/hr \hfill cyu@monmouth.edu
	\begin{itemize}  \itemsep -2pt
		\item Developing Java systems from the ground up.
		\item Managing small development teams.
		\item Developing tools for image/sound manipulation and video/audio compression.
	\end{itemize}
	
	{\sl Software Researcher} \hfill Summer 2010 \\
	Monmouth University \hfill William Tepfenhart\\
	Pay Rate: Approx. \$10/hr \hfill btepfenhart@monmouth.edu
	\begin{itemize}  \itemsep -2pt
		\item Interfacing with sparsely documented systems.
		\item Developing tools for audio manipulation, speech recognition, and equation parsing. 
	\end{itemize}

	{\sl Peer Tutor} \hfill Sept 2010 - May 2012 \\
	Monmouth University \hfill Dorothy Clearly\\
	Pay Rate: Approx. \$10/hr \hfill dcleary@monmouth.edu
	\begin{itemize}  \itemsep -2pt
		\item Experience explaining math and computer science concepts in simple terms.
		\item Solidified my understandings of core mathematics and C.S. concepts.
	\end{itemize}

\end{resume}
\end{document}




